---
title: "My R Markdown Primer"
author: "Wesley Huang"
date: "April 13, 2026"
output: html_document
---

# Introduction

R Markdown is a file format that lets you combine regular writing, R code, and formatted output in one document. It is useful because it keeps the explanation and the analysis together, which makes the work easier to follow and reproduce.

This is a simple example of narrative text written in Markdown. One helpful part of R Markdown is that it can mix normal paragraphs with code chunks and math expressions in the same file.

An inline math example is $\alpha + \beta = \gamma$.

A displayed equation example is:

$$
y = mx + b
$$

# Load Data

```{r}
library(ggplot2)
data(mtcars)
head(mtcars)
```

# Summary Statistics

The code chunk below gives a quick summary of the dataset.

```{r}
summary(mtcars)
```

# Visualization

The next code chunk creates a scatter plot showing the relationship between car weight and miles per gallon.

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(
    title = "Miles Per Gallon vs Car Weight",
    x = "Weight",
    y = "Miles Per Gallon"
  )
```

# Reflection

Using R Markdown was different from writing a plain report because it allowed me to keep my writing, code, and results together in one place. I liked that the output updated directly from the code, which makes the document more organized and reproducible. One thing I noticed is that formatting matters a lot, so even small mistakes in chunk syntax or Markdown symbols can affect the final output.