---
title: "My R Markdown Primer"
author: "Wesley Huang"
date: "April 13, 2026"
output: html_document
---

# Introduction

Before this assignment, I had never really used R Markdown, so I wasn’t too sure what to expect. From what I understand now, R Markdown is basically a way to combine your writing, code, and output all into one document. Instead of separating everything, you can keep it all in one place, which makes it a lot easier to follow.

One thing I noticed right away is how clean everything looks once it’s knitted. It feels more like a real report instead of just code in the console.

An inline math example is $\alpha + \beta = \gamma$.

A displayed equation example is:

$$
y = mx + b
$$

# Load Data

```{r}
library(ggplot2)
data(mtcars)
head(mtcars)
```

# Summary Statistics

The code below gives a quick summary of the dataset so we can see basic information about the variables.

```{r}
summary(mtcars)
```

# Visualization

Here I created a simple scatter plot to look at the relationship between car weight and miles per gallon.

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(
    title = "Miles Per Gallon vs Car Weight",
    x = "Weight",
    y = "Miles Per Gallon"
  )
```

# Reflection

After using R Markdown, I can see why it’s useful. Being able to combine everything into one document makes it much easier to stay organized, especially for assignments like this. At first, the formatting was a little confusing, but once I understood how the chunks and text work together, it started to make more sense. Overall, I think this is a better way to present work compared to writing everything separately.
